A few stickleback suffice to transport adaptive alleles to new lakes

### 2018-12-12 Stickleback_Paper.tex
plot twist

\begin{figure}
	\begin{center}
        \includegraphics[width=\textwidth]{Final_Plots/Fst_Genome_faa.pdf}
  		\caption{
		Average $F_{ST}$ in windows of 500Mb between:
        		\textbf{(top)} marine habitat and old lakes;
        		\textbf{(middle)} marine habitat and new lakes; and
        		\textbf{(bottom)} old and new lakes.
        		Each plot shows $F_{ST}$ values for a separate simulation,
        		with columns corresponding to increasing gene flow from left to right.
		Ten vertical dotted pink lines in each subplot 
        		show regions which have the potential to affect phenotype.
		All locations of pre-existing freshwater adapted alleles have been highlighted by 
		blue vertical lines with an alpha value of 0.3, so darker shades of blue imply more 
		freshwater adapted alleles at that location.
     } \label{fig:Fst}
	\end{center}
\end{figure}

>>>>

\begin{figure}
	\begin{center}
        \includegraphics[width=\textwidth]{Final_Plots/Fst_Genome_faa_pos.pdf}
  		\caption{
		Average $F_{ST}$ in windows of 500Mb between:
        		\textbf{(top)} marine habitat and old lakes;
        		\textbf{(middle)} marine habitat and new lakes; and
        		\textbf{(bottom)} old and new lakes.
        		Each plot shows $F_{ST}$ values for a separate simulation,
        		with columns corresponding to increasing gene flow from left to right.
		%Ten vertical dotted pink lines in each subplot 
        		%show regions which have the potential to affect phenotype.
		All locations of pre-existing freshwater adapted alleles have been highlighted by 
		pink dashed vertical lines with an alpha value of 0.3, so darker shades of blue imply more 
		freshwater adapted alleles at that location.
     } \label{fig:Fst}
	\end{center}
\end{figure}
